\documentclass{article}\usepackage[]{graphicx}\usepackage[]{color}
%% maxwidth is the original width if it is less than linewidth
%% otherwise use linewidth (to make sure the graphics do not exceed the margin)
\makeatletter
\def\maxwidth{ %
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother

\definecolor{fgcolor}{rgb}{0.345, 0.345, 0.345}
\newcommand{\hlnum}[1]{\textcolor[rgb]{0.686,0.059,0.569}{#1}}%
\newcommand{\hlstr}[1]{\textcolor[rgb]{0.192,0.494,0.8}{#1}}%
\newcommand{\hlcom}[1]{\textcolor[rgb]{0.678,0.584,0.686}{\textit{#1}}}%
\newcommand{\hlopt}[1]{\textcolor[rgb]{0,0,0}{#1}}%
\newcommand{\hlstd}[1]{\textcolor[rgb]{0.345,0.345,0.345}{#1}}%
\newcommand{\hlkwa}[1]{\textcolor[rgb]{0.161,0.373,0.58}{\textbf{#1}}}%
\newcommand{\hlkwb}[1]{\textcolor[rgb]{0.69,0.353,0.396}{#1}}%
\newcommand{\hlkwc}[1]{\textcolor[rgb]{0.333,0.667,0.333}{#1}}%
\newcommand{\hlkwd}[1]{\textcolor[rgb]{0.737,0.353,0.396}{\textbf{#1}}}%
\let\hlipl\hlkwb

\usepackage{framed}
\makeatletter
\newenvironment{kframe}{%
 \def\at@end@of@kframe{}%
 \ifinner\ifhmode%
  \def\at@end@of@kframe{\end{minipage}}%
  \begin{minipage}{\columnwidth}%
 \fi\fi%
 \def\FrameCommand##1{\hskip\@totalleftmargin \hskip-\fboxsep
 \colorbox{shadecolor}{##1}\hskip-\fboxsep
     % There is no \\@totalrightmargin, so:
     \hskip-\linewidth \hskip-\@totalleftmargin \hskip\columnwidth}%
 \MakeFramed {\advance\hsize-\width
   \@totalleftmargin\z@ \linewidth\hsize
   \@setminipage}}%
 {\par\unskip\endMakeFramed%
 \at@end@of@kframe}
\makeatother

\definecolor{shadecolor}{rgb}{.97, .97, .97}
\definecolor{messagecolor}{rgb}{0, 0, 0}
\definecolor{warningcolor}{rgb}{1, 0, 1}
\definecolor{errorcolor}{rgb}{1, 0, 0}
\newenvironment{knitrout}{}{} % an empty environment to be redefined in TeX

\usepackage{alltt}
\usepackage{Sweave}
\usepackage{float}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{siunitx}
\usepackage{mdframed}
\usepackage{natbib}
\bibliographystyle{..//refs/styles/besjournals.bst}
\usepackage[small]{caption}
\setkeys{Gin}{width=0.8\textwidth}
\setlength{\captionmargin}{30pt}
\setlength{\abovecaptionskip}{0pt}
\setlength{\belowcaptionskip}{10pt}
\topmargin -1.5cm        
\oddsidemargin -0.04cm   
\evensidemargin -0.04cm
\textwidth 16.59cm
\textheight 21.94cm 
%\pagestyle{empty} %comment if want page numbers
\parskip 7.2pt
\renewcommand{\baselinestretch}{1.5}
\parindent 0pt

\newmdenv[
  topline=true,
  bottomline=true,
  skipabove=\topsep,
  skipbelow=\topsep
]{siderules}
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\begin{document}

\renewcommand{\thetable}{\arabic{table}}
\renewcommand{\thefigure}{\arabic{figure}}
\renewcommand{\labelitemi}{$-$}

\section*{Lecture 8: 27 Sept 2018}
\textbf{Janet}
\begin{enumerate}
\item Why history in science?
  \begin{enumerate}
  \item helps us think about the way science changes over time. That is progresses and is not fixed. Science changes, is flexible and draws upon the thoughts and the societies with which it is generate. Helps us think about the place of science in a modern society. 
  \item Darwinian Revolution
   \begin{enumerate}
   \item Three major moments of scientific achievement: 1. Solar system - earth peripheral; 2. Humans in natural world - peripheral; 3. Freud and the mind and how the mind works.
   \item All unsettling revelations. Earth, Humans, the Mind. 
   \item Increasing evidence for darwinism. A number of faith-based structures retreated behind faith and isolated themselves from Darwinism.
   \item How was Darwinism globalized? Different forms, languages, interpretations, views. Didn't always adopt all of Darwin's points. Pick and choose aspects they wanted to adopt. 
   \end{enumerate}
  \item Why Wallace and Darwin happened at the same time?
    \begin{enumerate}
    \item Often said: Britain was industrializing nation at the time. Steam engines were first invented. This impact - transport that was faster than a horse - generated a sense of speed. Progress and innovation and change. Excitement. Newspapers, books, periodicals and magazines. Increase in steam-powered factory production. Textiles, newsprint. Production and manufacturers. At tremendous cost - health and child labor. Self-education and public education increased. Mechanics. Clocks and museums arose. Trinity (Diety) faith started to shift and become more diverse. Variety of beliefs. This directly aids Darwin and Wallace, helped dissipate the response. 
    \item Oliver Twist, workhouses. Colonial conquest. Great Exhibition 1851, greatness and progress of the British Nation. On display in Hyde Park `Crystal Palace' London. Darwin visits and is tremendously impressed. 
    \end{enumerate}
  \item Saw Darwinism as part of the industrializing world. Darwin was not the only evolutionists - Chambers, Herbert Spencer, obvi Wallace. Spencer had developmental view of human society. 
  \end{enumerate}
\end{enumerate}


\end{document}
